---
title: "iteration_and_listcols"
author: "Jiayi Shi"
date: "2022-11-01"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d


set.seed(1)
```

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```

```{r}
l$vec_numeric
```

```{r}
l[[1]]
```

```{r}
l[[1]][1:2]
```

```{r}
l[["mat"]]
```

## for loop

Given an input vector/list, apply a function to each element, save the result to a output vector/list.

```{r}
# input list
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  #list(mean = mean_x, sd = sd_x)
  # return a list
  
  tibble(
    mean = mean_x, 
    sd = sd_x
  ) # return a data frame
}
```

```{r}
output = vector("list", length = 4)
# how to create an empty list 
for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}

#same
output = map(list_norms, mean_and_sd)
output = map(.x = list_norms, ~ mean_and_sd(.x))
```

## map (function in `purr`, better than for loop, = `lappy` in base R)

```{r}
output = map(list_norms, mean_and_sd)
output
```

```{r}
output = map(list_norms, median)
output
```

* If know the output type, use map_* to simplify outputs.

```{r}
output = map_dbl(list_norms, median)#output is numeric
output
```

```{r}
output = map_df(list_norms, mean_and_sd)#simplified dataframe
output
```

* when your function has two arguments: map2_*
```{r}
output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))
```

## list, dataframe
list can contain anything:
list(a=...,b=...)

dataframe is a special kind of list, but with same length and printed as a table
data_frame(a=..., b=...)

## list column

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```

```{r}
listcol_df %>% pull(samp)
```

```{r}
mean_and_sd(listcol_df$samp[[1]])
```

## Nested data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_df %>% head()
```

The station name and id are constant across the year’s temperature and precipitation data. For that reason, we can reorganize these data into a new data frame with a single row for each station. Weather data will be separated into three station-specific data frames, each of which is the data “observation” for the respective station.

```{r}
weather_nest_df = 
  nest(weather_df, data = date:tmin)

weather_nest_df[["data"]]
```

unnesting
```{r}
weather_nest_df %>% 
  unnest(data)
```

```{r}
lm(tmax~tmin, data = weather_nest_df[["data"]][[1]])
lm(tmax~tmin, data = weather_nest_df[["data"]][[2]])
lm(tmax~tmin, data = weather_nest_df[["data"]][[3]])
```

* use map to simplify:

```{r}
weather_lm = function(df){
  lm(tmax~tmin, data = df)
}
```

```{r}
map(weather_nest_df[["data"]], weather_lm)
```

## Napoleon reviews
```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(url_base, 1:5)
```

```{r}
np_reviews = 
  tibble(
  page = 1:5,
  page_url = str_c(url_base, page)
  ) %>% 
  mutate(reviews = map(page_url, read_page_reviews)) %>% 
  select(-page_url) %>% 
  unnest(reviews)
```

```{r}
output = map(vec_urls, read_page_reviews)
dynamite_reviews = bind_rows(output)
```

